Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-29 paper/paper-mainfile.tex
remove unnecessary reference to HTN2SAS

Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case. % Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution. In fact, the state-of-the-art panda$_\pi$ planner and \cite{HTN2SAS} both use a compilation to classical planning, another decidable planning class.
In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems. We prove that when certain criteria are met, it guarantees that at least one solution will be preserved. 
Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion. Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.

@@

We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
%Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. 
We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem. The same setting is used for re-runs. For other planners, panda$_\pi$ with rc2(Add) is used for re-runs. We also test the latest version of TOHTN planners HTN2SAS, HyperTensioN and Lilotane on the transformed problems. Re-runs use panda$_{\pi}$ with the best heuristic(Add). 
We test both Complex and Simple Inference for linearization.

@@

%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
%		& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\

\todo{proven unsolvable should not be in superscripts}

>>>>

Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case. % Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems. We prove that when certain criteria are met, it guarantees that at least one solution will be preserved. 
Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion. Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.

@@

We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
%Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. 
We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem. The same setting is used for re-runs. For other planners, panda$_\pi$ with rc2(Add) is used for re-runs. We also test the latest version of TOHTN planners HyperTensioN and Lilotane on the transformed problems. Re-runs use panda$_{\pi}$ with the best heuristic(Add). We test both Complex and Simple Inference for linearization. Note that Complex Inference can only be inferred on grounded problems, but Lilotane and HyperTensioN are lifted planners.

@@

%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\

%\todo{proven unsolvable should not be in superscripts}
